### 2017-04-05 paper/evaluation.tex
pass on RQ2

We tooke the following actions to isolate our environment from
measurement noise.  First, we observed that some test tasks called
test-unrelated tasks (\eg, \emph{javadoc} generation and static
analyses) that could interfere in our time measurements.  To address
that potential issue, we inspected Maven execution logs from a sample
including a hundred projects prior to running the script from
Figure~\ref{fig:mvn-execution}.  The tasks we found were ignored from
execution (lines 1-3).  Furthermore, to avoid noise from operating
system events, we configured our workstation to run only essential
services.  The machine was dedicated to our experiments and we
accessed it via SSH. In addition, we configured the \CodeIn{isolcpus}
option from the Linux Kernel \cite{linux-kernel} to isolate six
virtual CPUs to run our experiments, leaving the remaining CPUs to run
OS processes~\cite{isolcpus-use}.  The rationale for this decision is
to prevent context-switching between user processes (running the
experiment) and OS-related processes.  Finally, to make sure our
measurements were fair, we compared timings corresponding to the
sequential execution of tests using Maven with that obtained with
JUnit's default \CodeIn{JUnitCore} runner, invoked from the command
line.  Results were very close.

@@

Section~\ref{sec:rqA} showed that medium and long-running projects are
not uncommon; they account to nearly \percentMedLongRunning{} of the
\numSubjs{} projects we analyzed.  This reveals the importance to
speedup test execution not only to huge projects as those from
Google~\cite{google-tap,google-ci} and
Microsoft~\cite{prasad-shulte-ieee-microsoft-ci}.  However, use of
parallelism does not imply speedups.  One sensible factor that is
important to the effectiveness of low-level parallelism is the
distribution of test costs in the test suite.  In the limit, if cost
is dominated by a single test, it is unlikely that parallelization
will be beneficial as a test method is the smallest working unit in
test frameworks (see Section~\ref{sec:frameworks}).

\begin{figure}[t]
    \centering
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group.}
    \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-medium.pdf}
      \caption{\label{fig:medtcost}Medium group.}
    \end{subfigure}
    %% \vspace{2ex}
    %% \begin{subfigure}{0.5\textwidth}
    %%   \centering
    %%   \begin{tabular}{rrrr}
    %%     \toprule
    %%     & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
    %%     \midrule    
    %%     Long   &  7 & 15 & 12 \\
    %%     Medium & 22 & 19 & 7 \\
    %%     \bottomrule
    %%   \end{tabular}
    %%   \caption{\label{fig:sd}Standard deviation ($\sigma$) of test case running times.}
    %% \end{subfigure}
    \caption{\label{fig:time-distributions}Time distributions.}%
\end{figure}

\sloppy Figures~\ref{fig:longtcost} and~\ref{fig:medtcost} show the
time distribution of individual test cases per project.  We observed
that the average median value of execution cost for a test was
relatively small (dashed horizontal red lines), namely 0.31s for
\medg{} projects and 0.23s for \longg{} projects.  The standard
deviations associated with each distribution were relatively
low.\Comment{ Figure~\ref{fig:sd} shows the number of projects within
  specific ranges of $\sigma$ values.}  Note that high standard
deviations may or may not be indicative of monopolization of execution
by a small number of tests.  For example, the highest value of
$\sigma$ occurred in \CodeIn{uber\_chaperone}, a project from the
medium group.  This project contains only \Fix{65} tests, \Fix{62} of
which take less than \Fix{0.5s} to run, \Fix{1} of which takes nearly
\Fix{3s} to run, and \Fix{2} of which take \Fix{40m} to run.  This is
an example where test suite parallelization may not be very beneficial
as \Fix{$>$99\%} of the execution cost is dominated by only \Fix{3\%}
of the tests.  Without these two tests this project would have been
classified as short-running.  A closer inspection in the data
indicates that the project \CodeIn{uber\_chaperone} was an extreme
case.  We did not find projects with similar characteristics of time
monopolization.  Project \CodeIn{facebookarchive\_linkbench} is
classified as long-running and has the second highest value of
$\sigma$.  For this project, however, cost is distributed more
smoothly across \Fix{529} tests, of which \Fix{119 (23\%)} take more
than \Fix{1s} to run.

@@

Figure~\ref{fig:time-distributions} showed that the average median
times were similar.  A closer inspection on results indicates that the
difference in overall running times across projects in these groups is
mainly justified by the number of test cases.
Figure~\ref{fig:size-testsuites} shows the difference in the
distribution of test suite sizes across groups.\Mar{$\leftarrow$ show
  stats to indicate discrimination of two distributions} Furthermore,
we also noted a strong positive correlation between running time and
number of test on projects in the \longg{} group.  The positive
correlation between these two variables was, however, weak in the
\medg{} group, suggesting that saving time in this group with test
suite parallelization may be more challenging as relatively fewer
tests dominate overall execution time.  Figure~\ref{fig:scattercost}
shows these results.

>>>>

We took the following actions to isolate our environment from
measurement noise.  First, we observed that some test tasks called
test-unrelated tasks (\eg, \emph{javadoc} generation and static
analyses) that could interfere in our time measurements.  To address
that potential issue, we inspected Maven execution logs from a sample
including a hundred projects prior to running the script from
Figure~\ref{fig:mvn-execution}.  The tasks we found were ignored from
execution (lines 1-3).  Furthermore, to avoid noise from operating
system events, we configured our workstation to run only essential
services.  The machine was dedicated to our experiments and we
accessed it via SSH. In addition, we configured the \CodeIn{isolcpus}
option from the Linux Kernel \cite{linux-kernel} to isolate six
virtual CPUs to run our experiments, leaving the remaining CPUs to run
OS processes~\cite{isolcpus-use}.  The rationale for this decision is
to prevent context-switching between user processes (running the
experiment) and OS-related processes.  Finally, to make sure our
measurements were fair, we compared timings corresponding to the
sequential execution of tests using Maven with that obtained with
JUnit's default \CodeIn{JUnitCore} runner, invoked from the command
line.  Results were very close.

@@

Section~\ref{sec:rqA} showed that medium and long-running projects are
not uncommon, accounting to nearly \percentMedLongRunning{} of the
\numSubjs{} projects we analyzed.  It is therefore important to
speedup regressing testing in open-source projects.\Comment{not only
  to huge projects as those from Google~\cite{google-tap,google-ci}
  and Microsoft~\cite{prasad-shulte-ieee-microsoft-ci}.}

Research question \numRQB{} assesses whether parallelism can help in
those cases.  One important factor to the effectiveness of parallelism
is the distribution of test costs in the test suite.  In the limit, if
cost is dominated by a single test from a large test suite, it is
unlikely that parallelization will be beneficial as a test method is
the smallest working unit in test frameworks.  However, avoiding
frequent context switches is another factor to consider.  For example,
assuming there are at least two CPUs available for execution, cost can
be cut in half if two tests in a large test suite dominate execution
time. For the case where cost is distributed more evenly across test
cases, one expects that speedups will be a function of the number of
cores.

%% These contradictory forces, pushing number of tests and cost
%% of each test up and down, make prediction of effectiveness challenging.

\begin{figure}[h]
    \centering
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group.}
    \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-medium.pdf}
      \caption{\label{fig:medtcost}Medium group.}
    \end{subfigure}
    %% \vspace{2ex}
    %% \begin{subfigure}{0.5\textwidth}
    %%   \centering
    %%   \begin{tabular}{rrrr}
    %%     \toprule
    %%     & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
    %%     \midrule    
    %%     Long   &  7 & 15 & 12 \\
    %%     Medium & 22 & 19 & 7 \\
    %%     \bottomrule
    %%   \end{tabular}
    %%   \caption{\label{fig:sd}Standard deviation ($\sigma$) of test case running times.}
    %% \end{subfigure}
    \caption{\label{fig:time-distributions}Time distributions.}%
\end{figure}

\sloppy Figures~\ref{fig:longtcost} and~\ref{fig:medtcost} show the
time distribution of individual test cases per project.  We observed
that the average median value of execution cost for a test was
relatively small (dashed horizontal red lines), namely 0.31s for
\medg{} projects and 0.23s for \longg{} projects.  The standard
deviations associated with each distribution were relatively
low.\Comment{ Figure~\ref{fig:sd} shows the number of projects within
  specific ranges of $\sigma$ values.}  We noted a small number of
cases of CPU monopolization.  For example, the highest value of
$\sigma$ occurred in \CodeIn{uber\_chaperone}, a project from the
medium group.  This project contains only 65 tests, 62 of which take
less than 0.5s to run, one of which takes nearly 3s to run, and two of
which take $\sim$40m to run.  For this project, 99.2\% of the
execution cost is dominated by only 3\% of the tests; without these
two costly tests this project would have been classified as
short-running.  A closer inspection in the data indicates that the
project \CodeIn{uber\_chaperone} was a corner case: we did not find
projects with such extreme time monopolization profile.  Project
\CodeIn{facebookarchive\_linkbench} is also classified as long-running
and has the second highest value of $\sigma$.  For this project,
however, cost is distributed more smoothly across \Fix{529} tests, of
which \Fix{119 (23\%)} take more than \Fix{1s} to run with the rest of
the tests running faster.

@@

%\Mar{$\leftarrow$ show stats to indicate discrimination of
%  two distributions}

Figure~\ref{fig:time-distributions} showed that the average median
times were similar.  A closer inspection on results indicates that the
difference in overall running times across projects in these groups is
mainly justified by the number of test cases as opposed to the
individual costs of test cases.  Figure~\ref{fig:size-testsuites}
shows the difference in the distribution of test suite sizes across
groups.  This figure indicates that long projects, albeit having a
wider inter-quartile range (middle 50\% projects in this group are
less predictable), have a higher median and much higher averages.
Furthermore, we noted a strong positive correlation between running
time and number of test on projects in the \longg{} group.  The
positive correlation between these two variables was, however, weak in
the \medg{} group, suggesting that saving time in this group with test
suite parallelization may be more challenging as relatively fewer
tests dominate overall execution time.  Figure~\ref{fig:scattercost}
shows these results.
